Phylogeographic inference with microtellite and SNPs

### 2019-05-09 code/rmarkdown/article.Rmd
cleaning all files

```

# MANUSCRIPT INFORMATION

@@

# ABSTRACT

# 1 | INTRODUCTION

# 2 | MATERIALS AND METHODS

@@

Miguel Camacho-Sanchez: 0000-0002-6385-7963 \newline
Guillermo Velo-Antón: 0000-0002-9483-5695 \newline
Ana Veríssimo: 0000-0003-3396-9822 \newline
JEFF ADAM PEDRO?
Silvia B. Carvalho: 0000-0003-4368-4708 \newline

>>>>

```
# Manuscript information

Format: add journal title  \newline
Abstract word count: xx \newline
Main word count: xx  \newline
Number of references: xx  \newline
Number of figures: xx  \newline
Number of tables: xx  \newline
Number of text boxes: xx  \newline
Number of equations: xx  \newline
Keywords: microtellites, DArTseq, SNPs, neighbour joining, structure, phylogeography, Hyla molleri, Pelobates cultripes, Iberian Peninsula   \newline
Spelling: British English (en-GB)   \newline
\clearpage

# Abstract

@@

# 1. Introduction
**general overview about the usat vs snp**
1-which are the characteristics of each marker
2-how informative are they
3-pros and cons for both
4-limitations
5-previous studies focusing on usats vs SNPs
**our case study**
1-study species: characteristics, distrigution, why them
2-markers datasets
**brief methodology with results and conclusions**

# 2. Materials and Methods
## 2.1 Data collection
Our analysis are built upon microsatellite and SNP datasets for two Iberian amphibians: *Hyla molleri* and *Pelobates cultripes*. For each species, the microtellite and SNP datasets come from different sample sets but covering both most of their native range (Figure 1).
The microsatellite genotypes were taken from already-published studies. For *Hyla molleri*, we gathered the microsatellite genotypes from *Appendix 1* in Sánchez-Montes et al. (2019). They consisted of `r adegenet::nInd(gen$usat_hyla)` samples with `r adegenet::nLoc(gen$usat_hyla)` genotyped microsatellites. For *Pelobates cultripes*, we requested the genotypes to the authors in Gutiérrez-Rodríguez et al. (2017). This dataset consisted of `r adegenet::nInd(gen$usat_pelo)` samples with `r adegenet::nLoc(gen$usat_pelo)` genotyped microsatellites.
The SNP data was generated using DArTseq technology (xx).
##

@@

Miguel Camacho-Sanchez: 0000-0002-6385-7963 \newline
Guillermo Velo-Antón: 0000-0002-9483-5695 \newline
Ana Veríssimo: 0000-0003-3396-9822 \newline
Jeffrey O. Hanson: 0000-0002-4716-6134
Adam Marques: 0000-0002-6070-0506
Silvia B. Carvalho: 0000-0003-4368-4708 \newline
